VM-Centric Snapshot Deduplication\\ for Cloud Data Backup

### 2015-05-08 snapshot_system/mass_eval.tex
minor changes

\section{Evaluation}
\label{sect:evaluation}
We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
Our implementation is based on the Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
Our evaluation objective is to
study deduplication efficiency and resource usage of VC,  
and assess its processing time and backup throughput, and  
the benefit in fault tolerance. 
We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on the previous work~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function~\cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine 
locally~\cite{extreme_binning09}.
%MSST-CHANGE-BEGIN
While this VO approach is designed for general deduplication and data backup,
we choose this VO approach as a baseline to compare because the other
approaches would have  a similar level of computing resource usage.
%MSST-CHANGE-END

>>>>

\section{Evaluation}
\label{sect:evaluation}
We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
8-core 3.1Ghz AMD FX-8120 and 16 GB RAM. 
Our implementation is based on the Alibaba cloud platform~\cite{Aliyun,WeiZhangIEEE}
and the underlying DFS uses  QFS with default replication degree 3 while the PDS replication degree is 6.
Our evaluation objective is to
study deduplication efficiency and resource usage of VC,  
and assess its processing time and backup throughput, and  
the benefit in fault tolerance. 
We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on the previous work~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function~\cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine 
locally~\cite{extreme_binning09}.
%MSST-CHANGE-BEGIN
While this VO approach is designed for general deduplication and data backup,
we choose it as a baseline for comparison because the other
approaches would have  a similar level of computing resource usage.
%MSST-CHANGE-END
